Parameter Space Representation of Pareto Front to Explore Hardware-Software Dependencies

### 2014-07-27 algorithm.tex
AA: prima parte finalizzata, manca solo di una lettura complessiva

Each iteration is called \emph{era}. The $i$-th era is characterized by: 
	\begin{itemize}
	\item the set of regions $\mathcal{R}_{i}$ in which the configuration space
	$mathcal{C}(S)=V_{1}\times\dots\times V_{n}$ is partitioned
	\item an approximation $\mathscr{P}_{i}$ of the Pareto-optimal set.
	\item a set $test_{i}$ of at most $K$ configurations evaluated
	in the era.
	\end{itemize}
$K$ is a parameter that must be set before the algorithm runs.
\comment{Spiegare un po' l'impatto di K. DP: se c'e' tempo...} Note that $\mathcal{R}_{i}$ is a partition of the configuration space, i.e.
	\begin{align}\begin{array}{l}
		\bigcup_{R\in\mathcal{R}_i} R = \mathcal{C}(S) \mbox{ and}\\
		R' \cap R'' = \emptyset, \forall R',R'' \in \mathcal{R}_i
	\end{array}\end{align}

@@

\item The goal of this step is preparing the regions that will compose the configuration space partition of the next era, i.e. $\mathscr{R}_{i+1}$. The following operations are performed:
	\begin{enumerate}
		\item Each high innovation region $R\in\mathscr{R}_{i,h}$ is split obtaining $\psi(R)$, as stated in def \defR{splitting-a-region}. We denote with $\psi\left(\mathscr{R}_{i,h}\right)$ the set of regions obtained as explained.
		\item Low innovation regions are left unchanged.
		\item No innovation regions are merged, two by two. To do so, pairs of no innovation contiguous regions $(R_1,R_2)$ are selected. We denote the set of these pairs as $\mathscr{M}_i$. This set is constructed such that pairs are independent, i.e. there cannot be two of them sharing a region. In other words, taking whatever $(R_1,R_2),(R_3,R_4) \in \mathscr{M}_i$, $R_i \neq R_j, \forall i,j\in\lbrace1,2,3,4\rbrace, i\neq$. 
We merge each pair of regions, i.e. $\forall (R_1,R_2)\in\mathscr{M}_i$ we calculate $\mu(R_1,R_2)$, according to \defR{merging-regions}.
We stress that the regions that belong to each selected pair must be contiguous, otherwise it is impossible to merge them. We denote with $\mu(\mathscr{M}_i)$ the set of the merged regions, i.e. $\mu(\mathscr{M}_i) = \bigcup_{(R_1,R_2)\in\mathscr{M}_i} \mu(R_1,R_2)$
	\end{enumerate}

\item The set of regions $\mathcal{R}_{i+1}$ for the following era is composed of the subregions resulting from splitting operations ($\psi\left(\mathscr{R}_{i,h}\right)$), the low innovation regions unchanged $\mathcal{R}_{i,l}$, the result of the merging operations ($\mu(\mathscr{M}_i))$ and the no innovation regions that was not possible to merge $\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left\{ R_{1},R_{2}\right\} \right)$. Formally:
	\[
	\mathcal{R}_{i+1}=
	\]
	\[
	=\psi\left(\mathscr{R}_{i,h}\right) \cup \mathcal{R}_{i,l}\cup
	\]
	\[
	\cup\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left\{ R_{1},R_{2}\right\} \right)\cup \mu(\mathscr{M}_i)
	\]
\end{enumerate}

@@

Observe that merging and splitting operation are dynamic processes. A portion
of the parameter space may be populated by a large number of small
regions in some eras, but can be covered by a small number of large
regions in next eras. This is a desirable property of PS, since, after a number
of eras of intense exploration of a portion of configuration space, this
exploration has turned to be enough thorough and so it may be time for
other portions to be minutely scanned.
\end{remark}

>>>>

Each iteration is called \emph{era}. The $i$-th era is characterized by: 
	\begin{itemize}
	\item the set of regions $\mathcal{R}_{i}$ in which the configuration space
	$mathcal{C}(S)=V_{1}\times\dots\times V_{n}$ is partitioned
	\item an approximation $\mathscr{P}_{i}$ of the Pareto-optimal set.
	\item a set $test_{i}$ of at most $K$ configurations evaluated
	in the era.
	\end{itemize}
$K$ is a parameter that must be set before the algorithm runs.
Note that $\mathcal{R}_{i}$ is a partition of the configuration space, i.e.
	\begin{align}\begin{array}{l}
		\bigcup_{R\in\mathcal{R}_i} R = \mathcal{C}(S) \mbox{ and}\\
		R' \cap R'' = \emptyset, \forall R',R'' \in \mathcal{R}_i
	\end{array}\end{align}

@@

\item The goal of this step is preparing the regions that will compose the configuration space partition of the next era, i.e. $\mathscr{R}_{i+1}$. The following operations are performed:
	\begin{enumerate}
		\item Each high innovation region $R\in\mathscr{R}_{i,h}$ is split obtaining $\psi(R)$, as stated in def \defR{splitting-a-region}. We denote with $\psi\left(\mathscr{R}_{i,h}\right)$ the set of regions obtained as explained.
		\item Low innovation regions are left unchanged.
		\item No innovation regions are merged, two by two. To do so, pairs of no innovation contiguous regions $(R_1,R_2)$ are selected. We denote the set of these pairs as $\mathscr{M}_i$. This set is constructed such that pairs are independent, i.e. there cannot be two of them sharing a region. In other words, taking whatever $(R_1,R_2),(R_3,R_4) \in \mathscr{M}_i$, $R_i \neq R_j, \forall i,j\in\lbrace1,2,3,4\rbrace, i\neq j$. 
We merge each pair of these regions, i.e. $\forall (R_1,R_2)\in\mathscr{M}_i$ we calculate $\mu(R_1,R_2)$, according to \defR{merging-regions}.
We stress that the regions that belong to each selected pair must be contiguous, otherwise it is impossible to merge them. We denote with $\mu(\mathscr{M}_i)$ the set of the merged regions, i.e. $\mu(\mathscr{M}_i) = \bigcup_{(R_1,R_2)\in\mathscr{M}_i} \mu(R_1,R_2)$
	\end{enumerate}

\item The set of regions $\mathcal{R}_{i+1}$ for the following era is composed of the subregions resulting from splitting operations ($\psi\left(\mathscr{R}_{i,h}\right)$), the low innovation regions unchanged $\mathcal{R}_{i,l}$, the result of the merging operations ($\mu(\mathscr{M}_i))$ and the no innovation regions that was not possible to merge $\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left\{ R_{1},R_{2}\right\} \right)$. Formally:
	\begin{align} 
	\mathcal{R}_{i+1} \triangleq
	\psi\left(\mathscr{R}_{i,h}\right) \cup \mathcal{R}_{i,l}\cup
	\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left\{ R_{1},R_{2}\right\} \right)\cup \mu(\mathscr{M}_i)
	\end{align}
\end{enumerate}

@@

Observe that merging and splitting operation are dynamic processes. A portion
of the parameter space may be populated by a large number of small
regions in some eras, but can be covered by a small number of large
regions in next eras. This is a desirable property of PS, since, after a number
of eras of intense exploration of a portion of configuration space, this
exploration has turned to be enough thorough and so it may be time for
other portions to be minutely scanned.

A pseudocode representation of PS algorithm is in Alg.\ref{alg:algo}

\begin{algorithm}[t]
	\small
	\caption{PS Algorithm}
	\label{alg:algo}
	  \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
	  \Input{S}
	  \Output{ $\tilde{\mathscr{P}}$ // Approximation of Pareto-set}
%
	  \nl //Initialization \\
	  \nl $\mathscr{R}_0\Leftarrow
				\left\{ V_{1}\times\dots\times V_{n}\right\} $; \\
	  \nl $\mathscr{P}_0\Leftarrow $ extract\_non\_dominated($test_0$);\\
	  \nl \\
	  \nl $i\Leftarrow 0$;\\
	  \nl \While{ !termination\_condition } {
			// Iteration steps\\
			\nl $test_i=\emptyset$;\\
	  		\nl \ForEach {$R \in \mathscr{R}_i$}{
				\nl $\mathscr{N}_{R,i} \Leftarrow$ configurations in $R$ not evaluated so far;\\
				\nl $|\mathscr{N}_{R,i}|\leq K/|\mathscr{R}_i|$? \\
						$\mbox{\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,}test_{R,i}\Leftarrow \mathscr{N}_{R,i}$:\\
						\mbox{\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,}$test_{R,i}\Leftarrow K/|\mathscr{R}_i|$ randomly selected configurations from $\mathscr{N}_{R,i}$;\\
			\nl $test_i\Leftarrow test_i \cup test_{R,i}$

			}

			\nl simulate ($test_i$);\\
			\nl $\mathscr{P}_i \Leftarrow 
				\mathscr{P}\left(test_{i}\cup\mathscr{P}_{i-1}\right)$;\\
			\nl \ForEach{$\mathbf{c}^*\in\mathscr{P}_i$} {
				\nl $is\left(\mathbf{c}^*\right) \Leftarrow \min\left\{ \left.s\left(\mathbf{c}\rightarrow\mathbf{c} \right)\right|\mathbf{c}\in\mathscr{P}_{i-1}\right\}$;\\
				}
			\nl \ForEach{$R\in\mathscr{R}_i$} {
				\nl $is\left(R\right)=\sum\left\{ \left.is\left(\mathbf{c}\right)\right|\mathbf{c}\in\mathscr{P}_{i}\cap R\right\} $;
			}

			\nl $is_{TOT,i}=\sum_{R\in\mathcal{R}_{i}}is\left(R\right)$ \\
			\nl $is_{av,i}=is_{TOT,i} / |\mathcal{R}_i|$\\
			\nl \\ //Region classification\\
			\nl $\mathcal{R}_{i,h}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)>\alpha\cdot is_{av,i-1}\right\}$; \\
			\nl $\mathcal{R}_{i,l}=\left\{ \left.R\in\mathcal{R}_{i}\right|0<is\left(R\right)\le\alpha\cdot is_{av,i-1}\right\} $; \\
			\nl $\mathcal{R}_{i,n}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)=0\right\} $;

			\nl \\ // Splitting and merging operations\\
			\nl $\psi(\mathscr{R}_{i,h}) \Leftarrow \lbrace 
					\psi(R) | R\in \mathscr{R}_{i,h}	
				\rbrace$; \\
			\nl construct $\mathscr{M}_i$; // the set of pair of contiguous no innovation regions \\
			\nl $\mu(\mathscr{M}_i) = \bigcup_{(R_1,R_2)\in\mathscr{M}_i} \mu(R_1,R_2)$;\\
			\nl\\ // Prepare the configuration space partition for the next iteration \\
			\nl $\mathcal{R}_{i+1} \triangleq
	\psi\left(\mathscr{R}_{i,h}\right) \cup \mathcal{R}_{i,l}\cup
	\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left\{ R_{1},R_{2}\right\} \right)\cup \mu(\mathscr{M}_i)$;\\
		}
	\nl $\tilde{\mathscr{P}} \Leftarrow \mathscr{P}_i$
\end{algorithm}
%

### 2014-07-27 paper.tex
AA: prima parte finalizzata, manca solo di una lettura complessiva

\usepackage{listings}

@@

\comment{AA: Esportare di
nuovo tutte le immagini libreoffice - svg - eps che viene meglio, come
si vede in \figR{3}. Aggiustare i nomi degli assi che in alcune figure
sono sbagliati. O forse basta esportarli col nuovo libreoffice che fa
meglio DP: hai ragione, ma forse siamo fuori tempo limite per queste
cose}

>>>>

\usepackage{listings}
\usepackage[ruled]{algorithm2e}

@@
